Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2021-04-14 analysis/paper/paper.Rmd
FLIP AXES FOR PEAK HAUL OUT vs EXTENT
per suggestion from Paul. Also adjusted the sea ice extent to smaller numbers and updated axis labels

peak_ho_df <- peak_ho_df %>% left_join(extent_max, 
                         by = "year") %>% 
  left_join(extent_lookup, by = c("date" = "fdate")) %>% 
  mutate(peak_diff_days = yday - max_extent_yday) %>% 
  distinct()

models <- peak_ho_df %>% 
  mutate(max_extent_km2 = max_extent_km2/1e6) %>% 
  group_by(species, age_sex) %>%  
  nest() %>% 
  mutate(model = map(data, ~ lm(max_extent_km2 ~ yday, data = .x))) %>% 
  mutate(glance = map(model, broom::glance)) %>% 
  unnest(glance)

@@

```{r maxextentHO, fig.height = 5.5, include=TRUE, fig.id = "maxextent", fig.cap="Annual timing of peak haul-out behavior analyzed against the yearly maximum area of sea ice extent in the study area. While spotted seal adult females and subadults show a negative trend line, none of the relationships were determined to be significant."}
ggplot(data = peak_ho_df, aes(x = yday, y = max_extent_km2, color = species)) + 
  geom_smooth(method = "lm", alpha = 0.2, aes(fill = species)) +
  geom_point() +
  facet_grid(age_sex~.) +
  scale_x_continuous(breaks = c(125,135,145, 156),
                     labels = c("05-May", "15-May", "25-May", "05-Jun")) +
  scale_color_manual(values = c('#E66100','#5D3A9B'), name = "") +
  scale_fill_manual(values = c('#E66100','#5D3A9B'), name = "") +
  theme(legend.position = "top",
        legend.justification = "right") +
  labs(x = "date of peak haul-out", y = "maximum sea ice extent (km^2 / 1e6)",
       title = "The connection between yearly maximum sea ice extent and the \ntiming of peak haul-out probability is limited")

>>>>

peak_ho_df <- peak_ho_df %>% left_join(extent_max, 
                         by = "year") %>% 
  left_join(extent_lookup, by = c("date" = "fdate")) %>% 
  mutate(peak_diff_days = yday - max_extent_yday) %>% 
  distinct() %>% 
  mutate(max_extent_km2 = max_extent_km2/1000)

models <- peak_ho_df %>% 
  group_by(species, age_sex) %>%  
  nest() %>% 
  mutate(model = map(data, ~ lm(max_extent_km2 ~ yday, data = .x))) %>% 
  mutate(glance = map(model, broom::glance)) %>% 
  unnest(glance)

@@

```{r maxextentHO, fig.height = 5.5, include=TRUE, fig.id = "maxextent", fig.cap="Annual timing of peak haul-out behavior analyzed against the yearly maximum area of sea ice extent in the study area. While spotted seal adult females and subadults show a negative trend line, none of the relationships were determined to be significant."}
ggplot(data = peak_ho_df, aes(y = yday, x = max_extent_km2, color = species)) + 
  geom_smooth(method = "lm", alpha = 0.2, aes(fill = species)) +
  geom_point() +
  facet_grid(age_sex~.) +
  scale_y_continuous(breaks = c(125,135,145, 156),
                     labels = c("05-May", "15-May", "25-May", "05-Jun")) +
  scale_color_manual(values = c('#E66100','#5D3A9B'), name = "") +
  scale_fill_manual(values = c('#E66100','#5D3A9B'), name = "") +
  theme(legend.position = "top",
        legend.justification = "right") +
  labs(y = "date of peak haul-out", x = "maximum sea ice extent (km^2 / 1000)",
       title = "The connection between yearly maximum sea ice extent and the \ntiming of peak haul-out probability is limited")
